\documentclass[letterpaper,11pt]{article}
\usepackage[sfdefault]{sourcesanspro} 
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt} % space at top
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}. #2 & \textit{\small#4} \\
       {\small #3} \\

    \end{tabular*}
    \vspace{-5pt}
}

 

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/davidrinck/}{\Large David Rinck}} & Email : \href{mailto:rinckd@gmail.com}{rinckd@gmail.com}\\
  \href{https://www.linkedin.com/in/davidrinck/}{https://www.linkedin.com/in/davidrinck} & Mobile : +1-917-684-8842 \\
\end{tabular*}



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Atonix}{Overland Park, KS}
      {Senior Software Engineer}{July 2020 - Present. June 2018 - May 2019 }
  
      \resumeItemListStart
        \resumeItem 
          {   Software startup that is a spinout of Black \& Veatch, a global engineering company. Leading the migration of a large 5 million+ lines of code legacy AngularJS and .NET Framework application into AWS Lambda Containers, .NET Core, and Angular. CI setup with Azure Devops for multiple angular applications and containers. }
          \resumeItem 
          {Migration of user authentication to AWS Cognito for integration with external identity providers (SAML).}
          \resumeItem 
          {Data Explorer. An interactive application for exploring alerts data and saving data visuzalizations. Built with Reactive Architecture - streams handle channels of communications for events, and react to each event.  }
      \resumeItemListEnd
      
    \resumeSubheading
      {Daupler}{Kansas City, MO}
      {Lead Software Engineer}{Sep 2019 - Aug 2020}
 
      \resumeItemListStart
        \resumeItem 
          {Techstars Kansas City Cohort. Designed classification method with Distilbert and Pytorch for labelling call descriptions. Classified if a call was for water or sewage, police, traffic, and if call was an emergency or not. Integrated with a front-end website so a human operator would be flagged if something was deemed an emergency, or the user could classify a call as an emergency (Human Assisted AI) }
        \resumeItem 
          {Designed Call Center application for taking city calls for water, sewer, and city services in Oakland, Durham, and other cities. Used the classification algorithm to route the call to the appropriate city department. }
        \resumeItem 
          {City Texting Utility. Users could select city regions by drawing polygons or selecting water system pressure zone or storm drainage basin on a map to send mass texts for boil orders, etc.}
      \resumeItemListEnd


    \resumeSubheading
      {symplr - Healthcare Compliance + Credentialing}{Overland Park, KS}
      {Lead Software Engineer}{May 2019 - Sep 2019}
      \resumeItemListStart
        \resumeItem 
          {Led a nearshore team to deliver SaaS application for the automation of pdf form filling of provider data. Used a microservice architecture with NodeJS, .NET Core and Kafka running on Kubernetes designed by Ben Capps (Stackify).  }
      \resumeItemListEnd

 
    \resumeSubheading
      {University of Kansas}{Overland Park, KS}
      {Data Analytics Instructor - Night Class }{Nov 2017 - Jun 2018}
      \resumeItemListStart
        \resumeItem 
        { Evening instructor for the Data Analytics Bootcamp at KU. It was a hands-on curriculum of Spark2, SQL, Python, Pandas, Scikit-learn, and Flask }
      \resumeItemListEnd

      \resumeSubheading
      {Homer Energy}{Boulder, CO}
      {Senior Software Engineer}{Aug 2013 - Sep 2018}
      \resumeItemListStart
        \resumeItem 
          { Started working there when it was a small startup. Successful exit to Underwriters Laboratories (UL). We took the core National Renewable Energy Laboratory algorithms for microgrid design, modernized them, and made the core decisions available through a Python / Matlab SDK so that researchers at ABB, Siemens, US Navy, and UL could interface with them. Also made an easy to use web or desktop interface using the same core code base. }
      \resumeItemListEnd
     
      \resumeSubheading
      {RBC Medical Innovations}{Lenexa, KS}
      {Embedded Software Engineer}{Oct 2012 - Aug 2013}
      \resumeItemListStart
        \resumeItem 
          { Member of software development team for FDA Class III life-saving medical device, the Philips V680 ventilator. }
          { Developed iPad app with Bluetooth LE connectivity to medical device. }
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


% %-----------PROJECTS-----------------
\section{Programming Skills}
  \resumeSubHeadingListStart

   \item{
     \textbf{Preferred Languages and Databases }{: Python, Javascript, Typescript, SQL Server, PostgreSQL }

   }
   \item{
    \textbf{Frameworks}{: Django, FastAPI, React, Angular, Flutter }

  }
 
  \resumeSubHeadingListEnd


  %-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Columbia University, School of Engineering and Applied Science;}{New York, New York}
    {Master of Science. Mechanical Engineering;  GPA: 3.63}{May 2011}
    {Our multidisciplinary research group created software for the Earth Institute. Designed a cloud-based data acquisition system for home energy monitoring with Python and Google App Engine.}
    \resumeSubheading
    {University of Missouri, Kansas City}{Kansas City, MO}
    {Bachelor of Science. Physics;  GPA: 3.9}{May 2009}
    {FIRST Robotics Team - Software Team Lead.}
    \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
% \section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
